Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2014-01-04 spie2014/spie2014.tex
done?'

@@

The texture mapping procedure in this paper was tested with three
different geometry-reconstruction methods, a PCA-based plane-fitting
method \cite{sanchez2012point}, a floor plan extrusion method
\cite{turnerfloorplan}, and a voxel-carving mesh generation method
\cite{turnerwatertight}. The first two methods generate very similar
low-resolution models, containing only major walls, ceilings and
floors. The third method generates high-resolution models, and
attempts to reconstruct all scanned objects in the
environment. Texture mapped models generated by the PCA-based, floor
plan extrusion, and voxel-carving approaches, can be seen in Figures
\ref{fig:pcaModels}, \ref{fig:fpModels}, and \ref{fig:voxelModels}
respectively.

\subsection{Runtime}
As mentioned earlier, our approach is quite efficient. The top wall in
Figure \ref{fig:indivPlanes}(a) was generated with 7543 $\times$ 776
pixels, and spans a 40-meter long wall. Given 41000 input images in
the entire dataset, a 2.8 GHz dual-core consumer-grade laptop takes
under a second to choose 36 candidate images, followed by a minute to
perform image projections, image alignment, and the shortest path
texturing method. The tile-caching approach takes roughly comparable
time, and over 75\% of the time for either method is spent on
calculating image projections, which are cached over multiple runs,
and also could be performed as a preprocessing step instead. While not
real-time, the process is capable of generating fast updates after
changes in various parameters or modifications to input data, and if
integrated directly into a 3D modeling system, could provide quick
visual feedback as data is collected.

>>>>

\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}} \\

  \centering \subfloat[][]{
    \includegraphics[height=2in, width=3in]{floorcropped.jpg} 
    \includegraphics[width=3in]{pier15floor.jpg}
  }
  \caption{Examples of our final texture mapping output for (a) walls,
    (b) ceilings, (c) floors}
  \label{fig:indivPlanes}
\end{figure}

@@

The texture mapping procedure in this paper was tested with three
different geometry-reconstruction methods, a PCA-based plane-fitting
method \cite{sanchez2012point}, a floor plan extrusion method
\cite{turnerfloorplan}, and a voxel-carving mesh generation method
\cite{turnerwatertight}. The first two methods generate very similar
low-resolution models, containing only major walls, ceilings and
floors. The third method generates high-resolution models, and
attempts to reconstruct all scanned objects in the
environment. Examples of individually textured regions are shown in
Figure \ref{fig:indivPlanes}, while fully texture mapped models
generated by the PCA-based, floor plan extrusion, and voxel-carving
approaches, can be seen in Figures \ref{fig:pcaModels},
\ref{fig:fpModels}, and \ref{fig:voxelModels} respectively.

\subsection{Runtime}
As mentioned earlier, our approach is quite efficient. The top wall in
Figure \ref{fig:indivPlanes}(a) is a single region, and its texture
was generated with 7543 $\times$ 776 pixels, spanning a 40 meter long
wall. Given 41000 input images in the dataset, a 2.8 GHz dual-core
machine takes under 10 seconds to choose 36 candidate images and
perform the full texturing process. The tile-caching approach takes a
similar amount of time as well, with the much larger floor textures in
Figure \ref{fig:indivPlanes}(c) taking 5-10 minutes to generate.
While not real-time, our process is capable of generating fast updates
after changes in various parameters or modifications to input data,
and if integrated directly into a 3D modeling system, could provide
quick visual feedback as data is collected.
